---
title: "SpongeBob SquarePants Episodes Report"
author: "Hayley Huang"
date: "`r Sys.Date()`"
output: html_document
params:
  production: TRUE
---

#Introduction and Analysis Objectives

The SpongeBob SquarePants Episodes Dataset contains detailed information about the popular TV show, including episode titles, air dates, production codes, season and episode numbers, running times, writers, U.S. viewership statistics, and character appearances. This dataset provides a rich source of information for analyzing various aspects of the show. The objectives of this analysis are to examine trends in viewership across storyboards, explore how episode characteristics evolve over time, and assess the contributions of different writers and artists to the success of the series.

```{r, set-chunk-opts, echo = FALSE, eval = params$production}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r, load-data}
here::i_am("SpongeBob_report.Rmd")

data <- readRDS(
  file = here::here("Clean_Data/cleaned_data.rds")
)
```

# Descriptive Analysis

## Storyboard Popularity analysis

The table below displays the viewer popularity for watching `r nrow(data)` storyboards from the SpongeBob SquarePants Episodes database.
```{r, table1}
table_one <- readRDS(
  file = here::here("Output/Table/table_one.rds")
)

table_one

```

## Graphical analysis

Below we present a bar plot showing the number of episodes created each year from 1998 to 2024.

```{r, plot-data}
#| fig.align = "center",
#| out.width = "1000px"

knitr::include_graphics(
  here::here("Output/Figure/barplot.png"))
  
```

